%-------------------------------------------------
% FileName: abstract-en.tex
% Author: MrLQQ
% Date: 2021-10-7
% Description: 英文摘要
% Others: 
% History: origin
%------------------------------------------------- 

% 以下不用改动-------------------------------------
% 断页
\clearpage
% 加入书签, bm@ABSTRACTNAME要唯一
\currentpdfbookmark{\defABSTRACTNAME}{bm@ABSTRACTNAME}
% \chapter*{} 表示不编号，不生成目录
% \markboth{}{} 用于页眉
% 此处以英文题目作为章题目


%\chapter*{\defTITLE \markboth{\defABSTRACTNAME}{}}
\thispagestyle{empty}

% 修改摘要和关键词---------------------------------
% 英文摘要
% 英文摘要与中文摘要的内容应一致。
\ABSTRACT{
Fourscore and seven years ago, our fathers brought forth upon this continent a new Nation, conceived in Liberty, and dedicated to the proposition that all men are created equal. Now, we are engaged in a great Civil War, testing whether that Nation, or any nation so conceived and so dedicated, can long endure. We are met on a great battlefield of that war. We have come to dedicate a portion of that field as a final resting-place for those who here gave their lives that that Nation might live. It is altogether fitting and proper that we should do this.

But, in a larger sense, we cannot dedicate, we cannot consecrate, we cannot hallow this ground. The brave men, living and dead, who struggled here, have consecrated it far above our poor power to add or detract. The world will little note nor long remember what we say here, but it can never forget what they did here. It is for us, the living, rather to be dedicated here to the unfinished work which they who fought here have thus far so nobly advanced. It is rather for us to be here dedicated to the great task remaining before us; that from these honored dead, we take increased devotion to that cause for which they gave the last full measure of devotion; that we here highly resolve that these dead shall not have died in vain, that this Nation, under GOD, shall have a new birth of freedom; and that government of the People by the People and for the People shall not perish from the earth.
}


% 英文关键词
% 每一个英文关键词都必须与中文关键词一一对应。
\KEYWORDS{Thesis; Hello world; Good luck; Congratulations}




 

